Multi-resolution Neural Field Estimation

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
caught a little typo

\cut{In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period. Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics. The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex. Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation. The key development in this paper is the multi-resolution decomposition forming the state-space model. The decomposition holds for more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.

Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions. Most importantly, future work should be directed towards applying and validating the framework on real data.}

>>>>

\cut{In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period. Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics. The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex. Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation. The key development in this paper is the multi-resolution decomposition forming the state-space model. The decomposition holds for more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.}

\cut{Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions. Most importantly, future work should be directed towards applying and validating the framework on real data.}
